\documentclass[11pt,a4paper,sans]{moderncv} 
\moderncvstyle{banking} 
\moderncvcolor{orange} 
\usepackage{lipsum} 
\usepackage[scale=0.75]{geometry} 


\firstname{Bachar}
\familyname{Bouazza}

\phone{+1 (514) 224-1942}
\email{bachar.bouazza@gmail.com}

\begin{document}

\recipient{HR Department}{} 
\date{\today} 
\opening{}  
\closing{Sincerely,} 
\enclosure[Encl]{curriculum vit\ae{}} 

\makelettertitle 
{I am writing in response to your job advertisement for the position: CRM Data Analyst, cited recently on indeed career web site.
}

{
By comparing my profile and background with your job description, I had a strong believe that I can be a good candidate for that position. 
I read through and understood the meaning and the implication of every keyword mentioned in the description.  
It is inline with my future career objective and  prospects: to work in an analytics environment where I can experiment with knowledge.
}

{As you can see, by leafing through my resume, I have a well diversified background in both academia and industry.  
I enjoy using my mathematical skills to model different kind of scientific problems in fields like economics, business processes analysis, finance, and machine learning.  
With good handling of vectorial, matrix,  tensorial notations and contractions used in multidimensional data analysis, calibration.  
Well versed in statistical models, probability, and operational research. 

My computer science background allows me to have a  good computing perspective working with data sets of multivariate type.  
I use, for instance, Python and R languages for scientific processing and analysis.  
I also use C++ as a low level object oriented language with good understanding of design patterns language and the new generic programming paradigm.
I can easily interact with different teams and able to understand different perspectives of different stack-holders, involved in a common project.
}

{
This is supported by over 15 years of field experience in many domains such as:
\begin{itemize}
	\item computational chemistry, drug discovery
	\item document classification, machine learning
	\item Market models, portfolio risk management
\end{itemize}
}


I have attached my résumé for your review and would welcome the opportunity to speak with you any time soon. 

\makeletterclosing


\end{document}